---
title: "infuse: A Quick Start Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{infuse: A Quick Start Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE,echo=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,       # Keep showing your code
  message = FALSE,   # Hides: "Loading required package", "Attaching core tidyverse", etc.
  warning = FALSE,    # Hides: "Warning in .recacheSubclasses..."
  collapse = TRUE,
  comment = "#>",
  fig.height = 5,
  fig.width = 7
)
library(infuse)
library(BuyseTest)
library(kableExtra)
library(data.table)
```


## Introduction

Suppose we have a Randomized Clinical Trial (RCT) with two groups (T= Treated and C= Controls). We use $X$ to refer to the outcome in the Treated group and $Y$ to the outcome in the Control group. Assuming higher values indicate superior clinical outcomes, we classify a random pair $(X,Y)$ based on a margin of clinical importance, $\lambda$:

* **Favorable**: if $X-Y\ge\lambda$
* **Neutral**: if $|X-Y|<\lambda$
* **Unfavorable**: if $X-Y\le\lambda$

The goal of the `infuse` package is to estimate the **Net Treatment Benefit (NTB)** and the **Win Ratio (WR)**

$$NB = P(X\ge Y+\lambda)-P(Y\ge X+\lambda) =P(\text{Favorable}) - P(\text{Unfavorable})$$


$$WR = \frac{P(X\ge Y+\lambda)}{P(Y\ge X+\lambda)} = \frac{P(\text{Favorable})}{P(\text{Unfavorable})} $$


### Efficient Estimation via Empirical Survival Functions

Rather than using computationally expensive pairwise comparisons, `infuse` uses **Empirical Survival Functions** $S_X^{n\ge}(x)$ and $S_Y^{m\ge}(y)$ to calculate the $P(X\ge Y+\lambda)$ and $P(Y\ge X+\lambda)$ and consequently:

$$NB =  \frac{1}{m} \sum_{j=1}^m S_X^{n\ge}(y_j + \lambda) - \frac{1}{n} \sum_{i=1}^n S_Y^{m\ge}(x_i + \lambda)$$

$$WR =  \frac{\frac{1}{m} \sum_{j=1}^m S_X^{n\ge}(y_j + \lambda) }{\frac{1}{n} \sum_{i=1}^n S_Y^{m\ge}(x_i + \lambda)}$$

This approach is mathematically equivalent to Generalized Pairwise Comparisons (GPC) but significantly faster for large sample sizes.



## Package Structure: The Infusion Lifecycle

The `infuse` package utilises a two-stage workflow:

1. `infuse()`: The foundation. It curates data, standardizes arms, and pre-calculates the influence values for favorable and unfavorable pairs. It returns a structured S3 object.

2. `realise()`: The engine. It calculates point estimates, influence-function-based standard errors, confidence intervals, and p-values for both individual and weighted Non-Prioritized Outcomes (NPO).


## First Example: Synthetic Score Analysis

We compare a "Wellness Score" between two groups of 60 participants, where a difference of at least 3 points is clinically meaningful.

```{r}
library(infuse)
library(data.table)
library(kableExtra)

set.seed(42)
dat <- data.table(
  Group = rep(c("Treated", "Controls"), each = 30),
  Score = c(rnorm(30, 105, 5), rnorm(30, 100, 5))
)

dat[sample(.N, 10)] |>  kbl() |>  kable_styling(full_width = FALSE)|>  kable_paper()
```


**Step 1: `infuse()`**

The `infuse()` function initializes the analysis. It identifies the treatment arm and pre-calculates the distribution of the data.

```{r}
# We specify that a "high" score is clinically better
s <- infuse(Score(3,high) ~ Group, data = dat, treated = "Treated")
```

- The formula object contains outcomes on the LHS that can be wrapped in function-like calls to specify clinical thresholds ($\lambda$) and direction (`high` or `low`). It supports multiple outcomes (joined by `+`) on the LHS and exactly one binary grouping variable on the RHS. In this example there is one outcome, `Score`, with a threshold defining the margin of clinical importance $\lambda = 3$, and `high` direction (meaning that high values represent superior outcomes). 

- The `treated` argument is a string specifying the level of the grouping variable to be treated as the "Treated" (Group X) arm. 

the object `s` is a structured S3 object of class `infuse`, a list containing three stacked `data.table`s:

* `data`: Patient-level data combined across all outcomes.

* `metadata`: Variable-level configurations and overall probabilities.

* `tail`: Generalized Pareto Distribution (GPD) tail extension parameters.

We can visualise the cumulative distribution functions of the Treated (X) and the Controls (Y) using the `plot` method:

```{r}
plot(s)
```

It is important to use the print method to revise that the function has correctly recognised the right inputs:

```{r}
print(s)
```

In this case we have one variable *Score* that is numeric with high values representing better outcomes and a threshold $\lambda = 3$. 

The summary method provides a high-level overview of the favorable/unfavorable probabilities::

```{r}
summary(s)
```

The mean score of the treated is 105 vs a mean score of the controls of 99 indicating an effect in favour of the Treated. The output also shows the probability that a random Treated-Control pair is Favorable and Unfavorable. In this example the probability of a **favorable** pair is 0.64 while the probability of an **unfavorable** pair is 0.14.

* The **Net Treatment Benefit (n)** is the difference 0.64 - 0.14 = 0.50.

* The **Win Ratio (w)** is the ratio: 0.64/0.14=4.6.

The `plotinf()` method helps identifying observations that are potentially **influential** in the estimation. We use the `vari = "f"` argument for *Favorable* summaries and `vari = "u"` for *Unfavorable* summaries:

```{r}
plotinf(s,vari = "f")
```

*Note: The diamonds represent the mean values of the influence functions, which are expected to be 0 for a correctly specified estimator*.

**Step 2: `realise()`**

We now "realise" the inference to get the formal statistical results. This converts the raw influence values into a tidy table with point estimates, confidence intervals, and p-values.


```{r, results = 'asis'}
h <- realise(s)
print(h)
#h |> kbl(caption = "Net Benefit Analysis (Threshold = 3)") |> kable_styling(bootstrap_options = "striped")
```

Both the Net Treatment Benefit NTB and the Win Ratio WR are statistically significant (p<0.05).

**Interpretation**:

- *NTB (0.50)*: in a set of 100 random treated-control pairs, we expect a net surplus of 50 favorable pairs over unfavorable pairs (concretely you expect 64 favorable pairs and 14 unfavorable pairs)

- *WR (4.7)*: A random treated-control pair is 4.7 times more likely to be favorable than to be unfavorable. 

- *GNNT (2)*: We expect to observe one extra favorable pair for every 2 random treated-control pairs.

A tidy version of the `realise` object can be obtained as follows:

```{r}
tab(h)
```


We compare these results with those obtained using Generalised Pairwise Comparisons:

```{r}
helper_buyse <- function(BT) {
  o1 <- as.data.table(confint(BT, statistic = "favorable"))[, Metric := "Favorable"]
  o2 <- as.data.table(confint(BT, statistic = "unfavorable"))[, Metric := "Unfavorable"]
  o3 <- as.data.table(confint(BT))[, Metric := "NetT Benefit"]
  o4 <- as.data.table(confint(BT, statistic = "winRatio"))[, Metric := "Win Ratio"]
  o <- rbind(o1[dim(o1)[1],],o2[dim(o2)[1],],o3[dim(o3)[1],],o4[dim(o4)[1],])
  row.names(o) <- NULL
  setDT(o)
  o <- o[, .( Metric,Estimate = estimate,SE = se,Lower = lower.ci,Upper = upper.ci, Pvalue = p.value)]
  o
}
BT <-  BuyseTest(data = dat,endpoint = "Score",type = "cont",treatment = "Group",threshold = 3,trace=0)

helper_buyse(BT) |> kbl() |>  kable_paper("hover", full_width = FALSE)
```

As one can see, the point estimates and standard errors are identical

## Real-World Example: The Obstetrics Dataset (Continuous)

### Background

This study investigated whether treating maternal periodontal disease reduces the risk of preterm birth and low birth weight. Periodontal disease is an inflammatory condition that may impact fetal health through the systemic release of cytokines.

In this randomized trial:

* Treatment (T): Received periodontal treatment and oral hygiene instruction.

* Control (C): Received brief oral exams only.

* Outcome: Birth weight of the baby (grams).

```{r}
data(obstetrics)
dat <- obstetrics

# Display sample data
kbl(head(dat)) |>  kable_paper(bootstrap_options = "striped", full_width = FALSE)
```

We define a clinically relevant difference of λ=500 grams. Any pair where the treated mother’s baby is at least 500g heavier than the control is considered "Favorable". 

```{r}
s <- infuse(Birthweight(500)~Group,data=dat,treated = "T")
print(s)
```

Note that by default the function chooses `high` values as being associated with superior outcomes. The plot of the Empirical CDFs allows us to see the "gap" between the two groups across the entire weight spectrum (which in this case is very small):

```{r}
plot(s)
```

Finally we get the estimates and the confidence intervals:


```{r, results = 'asis'}
h <- realise(s)
print(h)
#h |>  kbl(caption = "Net Benefit Analysis (Threshold = 500)") |>  kable_styling(bootstrap_options = "striped")
```

```{r}
tab(h)
```

### Benchmarking: `infuse` vs. `BuyseTest`

To validate the `infuse` engine, we compare our point estimates with the established `BuyseTest` package.

Initially, a direct comparison might show slight differences if the dataset contains missing values (NA). `BuyseTest` and `infuse` handle missingness differently by default. However, when we ensure a clean dataset, the results are very similar:

```{r}
BT <-  BuyseTest(data = dat |> na.omit(),endpoint = "Birthweight",type = "cont",treatment = "Group",threshold = 500,trace=0)
helper_buyse(BT) |>kbl() |> kable_paper("hover", full_width = FALSE)
```

### Why use `infuse`?

While both packages provide the same point estimates and similar standard errors, `infuse` utilizes influence functions to provide a significant speed advantage, especially when calculating confidence intervals for large datasets or multiple outcomes.

## Categorical & Binary Outcomes

A core strength of the `infuse` package is its mathematical consistency: it uses the exact same engine for continuous, binary, ordinal, and survival outcomes. This unification allows one to compare "Net Benefit" across different types of endpoints using a single framework as we will see in the last section. For now lets look at another example with a binary outcome. 

### **The `respiratory` dataset**

We use data from a clinical trial of 111 patients with respiratory illness. Patients were randomized to an Active (A) treatment or Placebo (P). Patients were examined at baseline and at four visits during treatment. We will focus on the respiratory status (`outcome` 1 = Good, 0 = Poor) at Visit 1.


```{r}
data(respiratory)
dat_v1 <- as.data.table(respiratory)[visit == 1, .(id, center, treat, sex, age, baseline, outcome)]

head(dat_v1) |> kbl() |> kable_paper("striped", full_width = FALSE)
```

**Step 1: Infuse and Visualize**

Note that for binary outcomes we specify the level that represents a better outcome, in this case 1:

```{r}
s <- infuse(outcome(1)~treat,data=dat_v1,treated = "A")
print(s)
```

By default, the function chooses a $\lambda = 0.5$ (this cannot be changed). When we "infuse" a binary outcome, the ECDF becomes a single-step function.


```{r}
plot(s)
```


Next, we estimate the relevant probabilities:

```{r, results = 'asis'}
h <- realise(s)
print(h)
#h |>  kbl(caption = "Net Benefit Analysis (Threshold = 0.5)") |>  kable_styling(bootstrap_options = "striped")
```

\

```{r}
tab(h)
```

\

**NTB as ARR**

For binary outcomes, the Net Treatment Benefit (NTB) is mathematically identical to the Absolute Risk Reduction (ARR). This provides a bridge between traditional epidemiology and the Win Statistics framework.

```{r}
means <- dat_v1[, .(risk = 1 - mean(outcome)), by = treat]
# Extract the values and calculate the difference
p_P <- means[treat == "P", risk]
p_A <- means[treat == "A", risk]

round(p_P - p_A, 4)
```

This result is why the **GNNT (Generalized Number Needed to Treat)** in `infuse` is calculated as 1/NTB, directly mirroring the traditional 1/ARR formula.


### Benchmarking: `infuse` vs. `BuyseTest`

We compare our point estimates with the `BuyseTest` package.

```{r}
BT <-  BuyseTest(data = dat_v1,endpoint = "outcome",type = "bin",treatment = "treat",trace=0, operator = "<0")
helper_buyse(BT) |>kbl() |> kable_paper("hover", full_width = FALSE)
```

### The Power of Custom Ordinal Outcomes

Standard binary analysis often ignores where a patient started. A "Good" outcome is more impressive if the patient started with a "Poor" baseline outcome. Because `infuse` is flexible, we can create a custom Composite Ordinal Outcome that captures the transition of health.

We define a 4-level scale of clinical improvement:

* **Level 1 (Worst)**: "Good" at _baseline_ $\longrightarrow$  "Poor" at _Visit 1_ (Deterioration).
* **Level 2**: "Poor" at _baseline_ $\longrightarrow$  "Poor" at _Visit 1_ (No change - Poor).
* **Level 3**: "Good" at _baseline_ $\longrightarrow$  "Good" at _Visit 1_ (Stable - Good).
* **Level 4 (Best)**: "Poor" at _baseline_ $\longrightarrow$  "Good" at _Visit 1_ (Recovery).


```{r}
# Create the variable using fcase and convert to ordered factor in one block
dat_v1 <- dat_v1[, combined_outcome := {
  # 1. Logic for levels
  res <- fcase(
    baseline == 1 & outcome == 0, "L1",
    baseline == 0 & outcome == 0, "L2",
    baseline == 1 & outcome == 1, "L3",
    baseline == 0 & outcome == 1, "L4"
  )
  # 2. Convert to ordered factor
  ordered(res, levels = c("L1", "L2", "L3", "L4"))
}]
```


**Analyzing the Recovery Scale**

We can now "infuse" this new 4-level variable.

```{r}
s <- infuse(combined_outcome(high)~treat,data=dat_v1,treated = "A")
print(s)
```

The `combined_outcome` is ordinal and by default, the function chooses a $\lambda = 1$ (this cannot be changed). High values are superior with `L4` being the best outcome. The following plot shows the empirical CDF for the active treatment (Blue) and Placebo (Red) of the newly defined outcome:

```{r}
plot(s)
```

```{r, results = 'asis'}
h <- realise(s)
print(h)
#h |> 
#  kbl(caption = "Net Benefit Analysis (Threshold = 1)") |> 
#  kable_styling(bootstrap_options = "striped")
```

\

```{r}
tab(h)
```

\
### Benchmarking with `BuyseTest`

To ensure accuracy, we compare these ordinal results with the `BuyseTest` package using the "continuous" type (which handles ordinal levels) and a threshold of 1.

```{r}
dat_v1[, combined_outcome_num := as.numeric(combined_outcome)]
BT <-  BuyseTest(data = dat_v1,endpoint = "combined_outcome_num",type = "cont",treatment = "treat",trace=0, threshold = 1,operator = "<0")
helper_buyse(BT) |>kbl() |> kable_paper("hover", full_width = FALSE)
```

Results match perfectly with `infuse` point estimates.


## Count Data (Ordinal Outcomes)

For count data, the calculations in infuse are identical to those for continuous outcomes. This is particularly useful in trials where the outcome is a frequency (e.g., number of events), as it allows for a clear interpretation of "improvement."

### The Epilepsy Dataset

This clinical trial investigated the effect of the anti-epileptic drug Progabide compared to a Placebo. 59 patients were monitored over four 2-week periods. We also have a baseline seizure count for the 8 weeks prior to randomization.

Our primary outcome is the reduction in seizures:

$$\text{Outcome}=\text{Baseline Count}−\sum(\text{Seizures in 4 Periods})$$

* A positive value indicates a reduction in seizures (Improvement).

* A negative value indicates an increase in seizures (Worsening).


```{r}
# Data preparation
# Convert to data.table
data(epilepsy)
dat <- epilepsy
setDT(dat)

# 1. Summarise: Calculate total seizures per subject
d1 <- dat[, .(total_seizures = sum(seizure.rate)), by = subject]

# 2. Select & Distinct: Get unique baseline info
d2 <- unique(dat[, .(subject, treatment, base)])

# 3. Join & Mutate: Merge and calculate reduction
dat_epi <- merge(d2, d1, by = "subject", all.x = TRUE)
dat_epi[, reduction := base - total_seizures]

# 4. Sample and Display
dat_epi[sample(.N, 5)] |> 
  kbl() |> 
  kable_paper("striped", full_width = FALSE)
```
\
In epilepsy trials, a small change in seizure count might be noise. We can set $\lambda$ to represent a clinically meaningful reduction. For example, let's say a "win" requires the Treated patient to have at least 5 fewer seizures than the Control patient. We also define "high" as good because we are measuring the reduction in seizures.

```{r}
s_epi <- infuse(reduction(5,high) ~ treatment, data = dat_epi, treated = "Progabide")
print(s_epi)
```

```{r}
plot(s_epi)
```


```{r, results = 'asis'}
h <- realise(s_epi)
print(h)
#h_epi |>  kbl(caption = "Seizure Reduction Analysis (Threshold = 5)") |>  kable_styling(bootstrap_options = "condensed")
```

\
```{r}
tab(h)
```

### Benchmarking with `BuyseTest`

We can verify these results against the standard pairwise approach. Note that for count data, we use type = "cont" (continuous) since the values are integers. 

```{r}
library(BuyseTest)
BT_epi <- BuyseTest(data = dat_epi, 
                    endpoint = "reduction", 
                    type = "cont", 
                    treatment = "treatment", 
                    threshold = 5, 
                    trace = 0)

# Compare point estimates
helper_buyse(BT_epi) |> kbl() |> kable_paper("hover", full_width = FALSE)
```


### Extension `epilepsy` dataset (Follow-up only)

In this analysis, we ignore the baseline values and focus exclusively on the total number of seizures recorded during the 8-week follow-up period. This "post-baseline only" approach is common when baseline data is unavailable or when the primary interest is the absolute state of the patient at the end of the study.

**Step 1: infuse() — Defining "Good" as Low**

Because we are measuring the number of seizures, a lower value represents a better clinical outcome. We specify this using the good = "low" argument. We keep our clinical threshold of $\lambda=5$. In this context, a treated patient "wins" if they have at least 5 fewer seizures than the control patient.

```{r}
s <- infuse(total_seizures(5,low) ~ treatment,data = dat_epi,treated = "Progabide")
print(s)
```

```{r}
summary(s)
```

```{r}
# The ECDF plot will now reflect that lower values are targeted for "wins"
plot(s)
```

**Step 2: realise() — Statistical Inference**

We generate the final estimates and confidence intervals.

```{r, results = 'asis'}
h <- realise(s)
print(h)
#h |>  kbl(caption = "Follow-up Seizure Rate Analysis (Threshold = 5, Lower is Better)") |>  kable_styling(bootstrap_options = "striped")
```


\
```{r}
tab(h)
```

\

**Interpretation and Comparison**

The "Reduction from Baseline" model (from the previous example) accounts for the fact that some patients start with very high seizure frequencies. By focusing only on the follow-up rate, we ignore the patient's starting point. If the groups were unbalanced at baseline, the results between these two methods would diverge significantly.


**Benchmarking: `infuse` vs. `BuyseTest`**

We validate these results against `BuyseTest`. Note that when using `BuyseTest` for "lower is better" outcomes with a threshold, we ensure the logic matches the infuse favorability settings.

```{r}
# Benchmarking raw seizure counts
# In BuyseTest, higher is better by default; 
# we use 'operator = "<0"' to indicate lower is better for a 'win'
BT_raw <- BuyseTest(data = dat_epi, 
                    endpoint = "total_seizures", 
                    type = "cont", 
                    treatment = "treatment", 
                    threshold = 5, 
                    operator = "<0",
                    trace = 0)

helper_buyse(BT_raw) |> 
  kbl(caption = "Comparison with BuyseTest (Follow-up Only)") |> 
  kable_paper("hover", full_width = FALSE)
```

This comparison confirms that the `infuse` influence-function engine correctly identifies "wins" based on the good = "low" parameter, yielding identical point estimates and standard errors to the traditional pairwise comparison method.


## Time-to-Event (Survival) Outcomes.

One of the greatest advantages of `infuse` is that it treats survival outcomes with the same mathematical engine as continuous data. By using the complement of the Kaplan-Meier estimator (1−KM) as the Empirical CDF, the package seamlessly integrates censoring into the NTB/WR framework.

### The `ipilimumab` Dataset

The aim of this study was to assess the use of ipilimumab after radiotherapy in patients with metastatic castration-resistant prostate cancer that progressed after docetaxel chemotherapy. Ipilimumab is a fully human monoclonal antibody that binds cytotoxic T-lymphocyte antigen 4 to enhance antitumour immunity. Participants were randomly assigned in a 1:1 ratio to receive bone-directed radiotherapy (8 Gy in one fraction) followed by either **ipilimumab** 10 mg/kg or **placebo** every 3 weeks for up to four doses. The outcome considered here was Progression-Free Survival in months (the censor indicator is `event`)

**Step 1: infuse() — The 1−KM Approach**

In `infuse`, survival outcomes are parsed using the standard `Surv(time, event)` syntax. Unlike continuous data where every observation "jumps" the ECDF by exactly $1/n$ (if no ties are present), survival data is more nuanced. The `infuse` engine uses the Kaplan-Meier product-limit formula to determine the size of the jumps.
\
In oncology, a tiny difference in PFS (e.g., 2 days) might not be clinically meaningful. If we set $\lambda=3$ months, a treated patient only "wins" the comparison if they remained progression-free for at least 3 months longer than the control patient.

```{r}
data(ipilimumab)
dat_surv <- ipilimumab

# infuse the survival data
# We specify 'good = "high"' because longer survival is better
s_surv <- infuse(Surv(time, event)(3,high) ~ arm, 
              data = dat_surv, 
              treated = "ipilimumab")
```


The `plot()` method for a survival infuse outcome displays the ECDF as $1−S_{KM}(t)$. 

```{r}
plot(s_surv)
```

**Step 2: realise() — Statistical Inference**

Because the engine is consistent, the output for survival data is identical in format to our previous examples.
\
```{r, results = 'asis'}
# Setting a 3-month clinical relevance threshold
h <- realise(s_surv)
print(h)
#h_surv |>  kbl(caption = "PFS Analysis (3-Month Threshold)") |>  kable_styling(bootstrap_options = "striped")
```
\
```{r}
tab(h)
```

\
**Benchmarking with BuyseTest**

We validate the `infuse` results against the `BuyseTest` package using the type = "timetoevent" endpoint. You will notice that the results are almost identical, confirming that the influence function approach for survival data is both accurate and robust.

```{r}
library(BuyseTest)
setDT(dat_surv)
dat_surv[, arm := factor(arm, levels = c("placebo", "ipilimumab"))]
BT_surv <- BuyseTest(data = dat_surv, 
                     endpoint = "time", 
                     type = "timetoevent",      # Specify survival type
                     status = "event",   # Specify censoring indicator
                     treatment = "arm", 
                     threshold = 3, 
                     trace = 0)

helper_buyse(BT_surv) |> 
  kbl(caption = "Comparison with BuyseTest (Survival Data)") |> 
  kable_paper("hover", full_width = FALSE)
```

**Summary of Survival Benefits**

By treating survival as an ECDF-based distribution (1−KM):

1. Consistency: You use the same functions for PFS as you do for Birthweight or Seizure counts.

2. Censoring Aware: The engine naturally accounts for censored data through the Kaplan-Meier weights.

3. Threshold Modeling: You can quantify "Net Treatment Benefit" in terms of time (months/days), providing an interpretation that is often more intuitive than a Hazard Ratio.


## Combining Multiple Outcomes: The Non-Prioritized Approach

In many trials, a treatment might be "good" for one outcome but "neutral" or even "bad" for another (e.g., an effective drug with side effects). To get a complete picture, we can combine multiple variables into a Global Net Treatment Benefit.

`infuse` uses the Non-Prioritized Outcome (NPO) approach. Instead of ranking outcomes in a strict hierarchy, we assign each one a clinical weight. The global result is a weighted average of the individual benefits.

### `obstetrics` Revisited: Efficacy + Safety

Let's combine two outcomes from the obstetrics dataset:

1. `PretermYN`: Whether the birth was preterm (0 = Yes, 1 = No). Here, `low` is good.

2. Birthweight: The weight of the baby. Here, high is good.

The threshold of $\lambda=0.5$ for the binary outcome is set by default and we set $\lambda=500g$ for birthweight.

```{r}
dat <- obstetrics
s_multi <- infuse(PretermYN("No ") + Birthweight(500) ~ Group, 
                data = dat, 
                treated = "T")

print(s_multi)
```


```{r, results = 'asis'}
# Step 2: realise with two lambdas
h <- realise(s_multi)
print(h)
#h_multi[order(Variable, Metric)] |>
#  kbl(caption = "Global Analysis: Preterm Birth & Birthweight") |>
#  kable_styling(bootstrap_options = "striped")
```


**Interpreting the "NPO" Row**

The `realise()` output adds a final row labelled NPO. This represents the "Global" treatment effect:

* **Global Net Benefit**: If the individual outcomes are $NB_{preterm}=0.10$ and $NB_{weight}=0.05$, an equally weighted NPO will result in a Global NB of 0.075.

* **Clinical Utility**: This NPO allows you to conclude whether the treatment is beneficial on balance, considering both the reduction in preterm births and the increase in birth weight simultaneously.

**Benchmarking NPO: `infuse` vs. `BuyseTest`**

To validate our global assessment, we compare the infuse NPO results with the `BuyseTest` package. While `BuyseTest` is often used for hierarchical (prioritized) testing, it can be configured to perform a weighted non-prioritized analysis by setting the weights for each endpoint.

```{r}
BT_npo <- BuyseTest(data = dat, 
                    formula = Group ~ bin(PretermYN,operator = "<0") + cont(Birthweight, threshold = 500,operator = ">0"),
                    #weightEndpoint = c(0.5, 0.5),      # Equal weights
                    hierarchical = FALSE , 
                    trace = 0)

# Use the helper to format and compare
helper_buyse(BT_npo) |> kbl() |> kable_paper("hover")
```


We can also use the `plot` method for the `realise` object:

```{r}
plot(h)
```

And also generate a nice output table using:

```{r,results="asis"}
tab(h)
```


**Customizing the "Clinical Voice"**

If clinicians believe that preventing a preterm birth is twice as important as the birth weight, you can easily adjust the weights in the `realise()` function:


```{r, results = 'asis'}
h <- realise(s_multi,w = c(0.70, 0.30))
print(h)
```

\
```{r}
tab(h)
```

\

```{r}
BT_npo <- BuyseTest(data = dat, 
                    formula = Group ~ bin(PretermYN,operator = "<0",weight=0.7) + cont(Birthweight, threshold = 500,operator = ">0",weight=0.3),
                    hierarchical = FALSE , 
                    trace = 0)

# Use the helper to format and compare
helper_buyse(BT_npo) |> kbl() |> kable_paper("hover")
```




