---
title: "infuse: A Quick Start Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{infuse_start_guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE,echo=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,       # Keep showing your code
  message = FALSE,   # Hides: "Loading required package", "Attaching core tidyverse", etc.
  warning = FALSE,    # Hides: "Warning in .recacheSubclasses..."
  collapse = TRUE,
  comment = "#>",
  fig.height = 5,
  fig.width = 5
)
```

```{r,echo=FALSE}
library(infuse)
library(BuyseTest)
library(kableExtra)
library(tidyverse)
```


## Introduction

Suppose we have a Randomized Clinical Trial (RCT) with two groups (T= Treated and C= Controls). We use $X$ to refer to the outcome in the Treated group and $Y$ to the outcome in the Control group. Without loss of generality, we assume higher values indicate a better outcome.

The experiment consists of selecting a random pair $(X,Y)$. These pairs are classified based on a clinically relevant difference, $\lambda$:

* **Favorable**: if $X-Y\ge\lambda$
* **Neutral**: if $|X-Y|<\lambda$
* **Unfavorable**: if $X-Y\le\lambda$

The objective is to estimate the **Net Treatment Benefit (NTB)**:

$$NB = P(X\ge Y+\lambda)-P(Y\ge X+\lambda) =P(\text{Favorable}) - P(\text{Unfavorable})$$

### Estimation via Empirical Survival Functions

To estimate $P(X\ge Y+\lambda)$ and $P(Y\ge X+\lambda)$, we use a plug-in estimator. Rather than comparing every possible pair (which is computationally expensive), we leverage the **Empirical Survival Functions** $S_X^{n\ge}(x)$ and $S_Y^{m\ge}(y)$:

$$NB =  \frac{1}{m} \sum_{j=1}^m S_X^{n\ge}(y_j + \lambda) - \frac{1}{n} \sum_{i=1}^n S_Y^{m\ge}(x_i + \lambda)$$

This approach is mathematically equivalent to Generalized Pairwise Comparisons (GPC) but significantly faster because it reduces the problem to a sequence of lookups on a step function.



## Package Structure: The Life of an Infusion

The `infuse` package operates on a simple, three-stage lifecycle. 
 
**sow(): Setting the Foundation**

The `sow()` function is your initialization tool. It prepares the environment, partitioning data into treatment/control groups, and pre-calculating Empirical Cumulative Distribution Functions (ECDF). It produces a structured S3 object optimized for the harvest function.

**harvest(): The Gathering Phase**

Once the seeds are sown, harvest() does the heavy lifting. It executes the core logic of the package. In essence it calculates the point estimates and the patient-level values of the influence functions. This function passes weighted ECDF data to the C++ inference engine to calculate point estimates and influence functions for Favorable and Unfavorable pairs, Net Treatment Benefit, Win Ratios and the Generalised Number Needed to Treat.

**reap(): Extracting the Essence**

The reap() function is the final step. It takes the raw output from the harvest() phase and "strains" it into a clean, usable format (like a tidy data frame or a summary list). It calculates point estimates, standard errors, confidence intervals, and p-values for NTB and WR statistics using Influence Functions. It supports both individual outcome analysis and a weighted Non-Prioritized Outcome (NPO) summary.


## First Example

In this synthetic example, we compare a "Score" (like a wellness index) between a Treated and Control group. To determine if a random Treated individual has a "Favorable" outcome compared to a random Control individual, we use a minimum difference of 3 points.

First, let's create a small dataset of 60 participants.

```{r}
library(infuse)
library(tidyverse)
library(kableExtra)

set.seed(42)
dat <- data.frame(
  Group = c(rep("Treated", 30), rep("Controls", 30)),
  Score = c(rnorm(30, 105, 5), rnorm(30, 100, 5))
)

dat %>% slice_sample(n=10) %>% kbl() %>% kable_paper()
```

**Step 1 sow(): The preparation**

The sow() function initializes the analysis. It identifies the treatment arm and pre-calculates the distribution of the data.

```{r}
# We specify that a "high" score is clinically better
s <- sow(Score ~ Group, data = dat, treated = "Treated", good = "high")
```

- The formula object `Score ~ Group` supports multiple outcomes on the LHS and exactly **one binary grouping variable on the RHS**.

- The `treated` argument is a string specifying the level of the grouping variable to be treated as the "Treated" (Group X) arm. Defaults to "Treated".

- Finally, the `good` argument is a character vector ("high" or "low") indicating clinical favorability. If `good = "high"` high values of the outcome represent better clinical response.

the object `s` is a structured S3 object of class `sow`, a nested list containing:

* `xid`, `yid`: Participant IDs for Treated (X) and Control (Y) groups.

* `Variables`: A named list for each outcome containing pre-calculated ECDFs, weights, and GPD tail parameters if applicable.

We can plot the cumulative distribution functions of the Treated (X) and the Controls (Y) using the `plot` method:

```{r}
plot(s)
```

The summary method:

```{r}
summary(s)
```

gives high level summaries. In this case we have one variable *Score* that is numeric with high values representing better outcomes and a mean of the treated of 105 vs a mean of the controls of 99 indicating an effect in favour of the Treated.

**Step 2: harvest() (The Calculation)**

Now we calculate the probability that a random Treated-Control pair is Favorable. We define `lambda = 3`, meaning a treated patient only "wins" against a control patient if their score is at least 3 points higher.

```{r}
# The harvest function runs the influence-function engine
h <- harvest(s, lambda = 3)
summary(h)
```

\

In this example the probability of a **favorable (f)** pair is 0.64 while the probability of an **unfavorable (u)** pair is 0.14.

* The **Net Treatment Benefit (n)** is the difference 0.64 - 0.14 = 0.50.

* The **Win Ratio (w)** is the ratio: 0.64/0.14=4.6 (which is 1.55 on the log-scale).

The `plot()` method helps identify observations that are potentially **influential** in the estimation:

```{r}
plot(h,metric="ntb",type = "influence")
```

*Note: The diamonds represent the mean values of the influence functions, which are expected to be 0 for a correctly specified estimator*.

**Step 3: reap() (The Results)**

Finally, we "reap" the statistical inference. This converts the raw influence values into a tidy table with point estimates, confidence intervals, and p-values.


```{r}
r <- reap(h)
r %>% 
  kbl(caption = "Net Benefit Analysis (Threshold = 3)") %>% 
  kable_styling(bootstrap_options = "striped")
```

Both the NTB and the WR ratio are statistically significant (p<0.05).

**Interpretation**:

- *NTB (0.50)*: in a set of 100 random treated-control pairs, we expect a net surplus of 50 favorable pairs over unfavorable pairs (concretely you expect 64 favorable pairs and 14 unfavorable pairs)

- *WR (4.7)*: A random treated-control pair is 4.7 times more likely to have a favorable pair than an unfavorable one. 

- *GNNT (2)*: We expect to observe one extra favorable pair for every 2 random treated-control pairs.

All in all, this analysis demonstrates that the treatment results in a significant and clinically meaningful benefit for the participants.

We compare the results with those obtained using Generalised Pairwise Comparisons:

```{r}
helper_buyse <- function(BT) {
  o1 <- confint(BT,statistic = "favorable") %>% mutate(Metric="Favorable")
  o2 <- confint(BT,statistic = "unfavorable") %>% mutate(Metric="Unfavorable")
  o3 <- confint(BT) %>% mutate(Metric="NetT Benefit")
  o4 <- confint(BT,statistic = "winRatio") %>% mutate(Metric="Win Ratio")
  o <- rbind(o1[dim(o1)[1],],o2[dim(o2)[1],],o3[dim(o3)[1],],o4[dim(o4)[1],])
  row.names(o) <- NULL
  o <- o %>% select(Metric,Estimate = estimate,Lower = lower.ci,Upper = upper.ci)
  o
}
BT <-  BuyseTest(data = dat,endpoint = "Score",type = "cont",treatment = "Group",threshold = 3,trace=0)

helper_buyse(BT) %>%kbl() %>% kable_paper("hover", full_width = FALSE)
```

We are ready now to see a few real life examples.


## Real-World Example: The Obstetrics Dataset (Continuous)

### Background

This study investigated whether treating maternal periodontal disease reduces the risk of preterm birth and low birth weight. Periodontal disease is an inflammatory condition that may impact fetal health through the systemic release of cytokines.

In this randomized trial:

* Treatment (T): Received periodontal treatment and oral hygiene instruction.

* Control (C): Received brief oral exams only.

* Outcome: Birth weight of the baby (grams).

```{r}
data(obstetrics)
dat <- obstetrics

# Display sample data
kbl(head(dat)) %>%
  kable_paper(bootstrap_options = "striped", full_width = FALSE)
```

### Distributions and Sowing

We define a clinically relevant difference of λ=500 grams. Any pair where the treated mother’s baby is at least 500g heavier than the control is considered "Favorable."

The plot of the Empirical CDFs allows us to see the "gap" between the two groups across the entire weight spectrum (which in this case is very small):

```{r}
s <- sow(Birthweight~Group,data=dat,treated = "T")
plot(s)
```

```{r}
summary(s)
```

### Harvesting and reaping the NTB, WR and GNNT

Using our $\lambda = 500$ threshold, we estimate the relevant probabilities:

```{r}
h <- harvest(s,500)
r <- reap(h)
r %>% 
  kbl(caption = "Net Benefit Analysis (Threshold = 500)") %>% 
  kable_styling(bootstrap_options = "striped")
```

### Benchmarking: `infuse` vs. `BuyseTest`

To validate the `infuse` engine, we compare our point estimates with the established `BuyseTest` package.

Initially, a direct comparison might show slight differences if the dataset contains missing values (NA). `BuyseTest` and `infuse` handle missingness differently by default. However, when we ensure a clean dataset, the results match perfectly:

```{r}
BT <-  BuyseTest(data = dat %>% na.omit(),endpoint = "Birthweight",type = "cont",treatment = "Group",threshold = 500,trace=0)
helper_buyse(BT) %>%kbl() %>% kable_paper("hover", full_width = FALSE)
```

### Why use `infuse`?

While both packages provide the same point estimates, `infuse` utilizes influence functions to provide a significant speed advantage, especially when calculating confidence intervals for large datasets or multiple outcomes.

## Categorical & Binary Outcomes

A core strength of the `infuse` package is its mathematical consistency: it uses the exact same engine for continuous, survival, and categorical outcomes. This unification allows researchers to compare "Net Benefit" across different types of endpoints using a single framework as we will see in the last section. For now lets look at another example with a binary outcome. 

### **The `respiratory` dataset**

We use data from a clinical trial of 111 patients with respiratory illness. Patients were randomized to an Active (A) treatment or Placebo (P). Patients were examined at baseline and at four visits during treatment. We will focus on the respiratory status (`outcome` 1 = Good, 0 = Poor) at Visit 1.


```{r}
data(respiratory)
dat_v1 <- respiratory %>% 
  dplyr::filter(visit == 1) %>% 
  select(id, center, treat, sex, age, baseline, outcome)

head(dat_v1) %>% kbl() %>% kable_paper("striped", full_width = FALSE)
```

**Step 1: Sow and Visualize**

When we "sow" a binary outcome, the ECDF becomes a single-step function.

```{r}
s <- sow(outcome~treat,data=dat_v1,treated = "A")
plot(s)
```

```{r}
summary(s)
```

### Harvesting and reaping 

Using the $\lambda = 0.5$ threshold (default for binary outcomes), we estimate the relevant probabilities:

```{r}
h <- harvest(s)
r <- reap(h)
r %>% 
  kbl(caption = "Net Benefit Analysis (Threshold = 0.5)") %>% 
  kable_styling(bootstrap_options = "striped")
```

**NTB as ARR**

For binary outcomes, the Net Treatment Benefit (NTB) is mathematically identical to the Absolute Risk Reduction (ARR). This provides a bridge between traditional epidemiology and the Win/Loss framework.

```{r}
p_P <- dat_v1 %>% dplyr::filter(treat == "P") %>% pull(outcome)
p_P <- 1-mean(p_P)
p_A <- dat_v1 %>% dplyr::filter(treat == "A") %>% pull(outcome)
p_A <- 1-mean(p_A)
round(p_P - p_A,4)
```

This result is why the **GNNT (Generalized Number Needed to Treat)** in `infuse` is calculated as 1/NTB, directly mirroring the traditional 1/ARR formula.


### Benchmarking: `infuse` vs. `BuyseTest`

We compare our point estimates with the `BuyseTest` package.

```{r}
BT <-  BuyseTest(data = dat_v1,endpoint = "outcome",type = "bin",treatment = "treat",trace=0, operator = "<0")
helper_buyse(BT) %>%kbl() %>% kable_paper("hover", full_width = FALSE)
```

### The Power of Custom Ordinal Outcomes

Standard binary analysis often ignores where a patient started. A "Good" outcome is more impressive if the patient started with a "Poor" baseline outcome. Because `infuse` is flexible, we can create a custom Composite Ordinal Outcome that captures the transition of health.

We define a 4-level scale of clinical improvement:

* **Level 1 (Worst)**: "Good" at _baseline_ $\longrightarrow$  "Poor" at _Visit 1_ (Deterioration).
* **Level 2**: "Poor" at _baseline_ $\longrightarrow$  "Poor" at _Visit 1_ (No change - Poor).
* **Level 3**: "Good" at _baseline_ $\longrightarrow$  "Good" at _Visit 1_ (Stable - Good).
* **Level 4 (Best)**: "Poor" at _baseline_ $\longrightarrow$  "Good" at _Visit 1_ (Recovery).


```{r}
dat_v1 <- dat_v1 %>% 
  mutate(combined_outcome = case_when(
    baseline == 1 & outcome == 0 ~ 1,
    baseline == 0 & outcome == 0 ~ 2,
    baseline == 1 & outcome == 1 ~ 3,
    baseline == 0 & outcome == 1 ~ 4
  ))
```


**Analyzing the Recovery Scale**

We can now "sow" this new 4-level variable. In the harvest step, we set $\lambda = 1$ to indicate that a "win" requires moving at least one level up on this scale.

The following plot shows the empirical CDF for the active treatment (Blue) and Placebo (Red) of the newly defined outcome:

```{r}
s_ext <- sow(combined_outcome~treat,data=dat_v1,treated = "A")
plot(s_ext)
```

```{r}
h_ext <- harvest(s_ext,lambda=1)
r <- reap(h_ext)
r %>% 
  kbl(caption = "Net Benefit Analysis (Threshold = 1)") %>% 
  kable_styling(bootstrap_options = "striped")
```

### Benchmarking with `BuyseTest`

To ensure accuracy, we compare these ordinal results with the `BuyseTest` package using the "continuous" type (which handles ordinal levels) and a threshold of 1.

```{r}
BT <-  BuyseTest(data = dat_v1,endpoint = "combined_outcome",type = "cont",treatment = "treat",trace=0, threshold = 1,operator = "<0")
helper_buyse(BT) %>%kbl() %>% kable_paper("hover", full_width = FALSE)
```

Results match perfectly with `infuse` point estimates.


## Count Data (Ordinal Outcomes)

For count data, the calculations in infuse are identical to those for continuous outcomes. This is particularly useful in trials where the outcome is a frequency (e.g., number of events), as it allows for a clear interpretation of "improvement."

### The Epilepsy Dataset

This clinical trial investigated the effect of the anti-epileptic drug Progabide compared to a Placebo. 59 patients were monitored over four 2-week periods. We also have a baseline seizure count for the 8 weeks prior to randomization.

Our primary outcome is the reduction in seizures:

$$\text{Outcome}=\text{Baseline Count}−\sum(\text{Seizures in 4 Periods})$$

* A positive value indicates a reduction in seizures (Improvement).

* A negative value indicates an increase in seizures (Worsening).


```{r}
# Data preparation
data(epilepsy)
d1 <- epilepsy %>% group_by(subject) %>% summarise(total_seizures = sum(seizure.rate))
d2 <- epilepsy %>% select(subject, treatment, base) %>% distinct()
dat_epi <- d2 %>% left_join(d1, by = "subject") %>% 
  mutate(reduction = base - total_seizures)

# Show a random sample of the processed data
dat_epi %>% sample_n(5) %>% kbl() %>% kable_paper("striped", full_width = F)
```

**Step 1: Sow the Seeds**

We define "high" as good because we are measuring the reduction in seizures.

```{r}
s_epi <- sow(reduction ~ treatment, data = dat_epi, treated = "Progabide", good = "high")

# The plot will show the step-like nature of count data ECDFs
plot(s_epi)
```

```{r}
summary(s_epi)
```


*### **Step 2: Harvest with Clinical Thresholds**

In epilepsy trials, a small change in seizure count might be noise. We can set $\lambda$ to represent a clinically meaningful reduction. For example, let's say a "win" requires the Treated patient to have at least 5 fewer seizures than the Control patient.

```{r}
# lambda = 5 seizures difference
h_epi <- harvest(s_epi, lambda = 5)
summary(h_epi)
```

**Step 3: Reap the Inference**

Finally, we calculate the Win Ratio and Net Treatment Benefit for this seizure reduction threshold.

```{r}
reap(h_epi) %>% 
  kbl(caption = "Seizure Reduction Analysis (Threshold = 5)") %>% 
  kable_styling(bootstrap_options = "condensed")
```

### Interpretation 

Unlike a standard Poisson regression or T-test on counts, the infuse output gives us a direct "patient-centered" probability:

1. Favorable Probability: The chance that a random patient on Progabide sees a better seizure reduction (by at least 5) than a random patient on Placebo.

2. Net Benefit: The overall "surplus" of winners. If the Net Benefit is 0.29, it means for every 100 random comparisons, you expect 29 more "successful" reductions in the treated group than in the control.

3. Win Ratio: The odds of picking a "winner" vs. a "loser" when comparing a random treated patient to a random control.
    
### Benchmarking with `BuyseTest`

We can verify these results against the standard pairwise approach. Note that for count data, we use type = "cont" (continuous) since the values are integers. 

```{r}
library(BuyseTest)
BT_epi <- BuyseTest(data = dat_epi, 
                    endpoint = "reduction", 
                    type = "cont", 
                    treatment = "treatment", 
                    threshold = 5, 
                    trace = 0)

# Compare point estimates
helper_buyse(BT_epi) %>% kbl() %>% kable_paper("hover", full_width = FALSE)
```


### Extension `epilepsy` dataset (Follow-up only)

In this analysis, we ignore the baseline values and focus exclusively on the total number of seizures recorded during the 8-week follow-up period. This "post-baseline only" approach is common when baseline data is unavailable or when the primary interest is the absolute state of the patient at the end of the study.

**Step 1: sow() — Defining "Good" as Low**

Because we are measuring the number of seizures, a lower value represents a better clinical outcome. We specify this using the good = "low" argument.

```{r}
s_raw <- sow(total_seizures ~ treatment, 
             data = dat_epi, 
             treated = "Progabide", 
             good = "low")

# The ECDF plot will now reflect that lower values are targeted for "wins"
plot(s_raw)
```

**Step 2: harvest() — Setting the Threshold**

We keep our clinical threshold of $\lambda=5$. In this context, a treated patient "wins" if they have at least 5 fewer seizures than the control patient.

```{r}
h_raw <- harvest(s_raw, lambda = 5)
summary(h_raw)
```

**Step 3: reap() — Statistical Inference**

We generate the final estimates and confidence intervals.

```{r}
r_raw <- reap(h_raw)

r_raw %>% 
  kbl(caption = "Follow-up Seizure Rate Analysis (Threshold = 5, Lower is Better)") %>% 
  kable_styling(bootstrap_options = "striped")
```

**Interpretation and Comparison**

The "Reduction from Baseline" model (from the previous example) accounts for the fact that some patients start with very high seizure frequencies. By focusing only on the follow-up rate, we ignore the patient's starting point. If the groups were unbalanced at baseline, the results between these two methods would diverge significantly.


**Benchmarking: `infuse` vs. `BuyseTest`**

We validate these results against `BuyseTest`. Note that when using `BuyseTest` for "lower is better" outcomes with a threshold, we ensure the logic matches the infuse favorability settings.

```{r}
library(BuyseTest)

# Benchmarking raw seizure counts
# In BuyseTest, higher is better by default; 
# we use 'operator = "<0"' to indicate lower is better for a 'win'
BT_raw <- BuyseTest(data = dat_epi, 
                    endpoint = "total_seizures", 
                    type = "cont", 
                    treatment = "treatment", 
                    threshold = 5, 
                    operator = "<0",
                    trace = 0)

helper_buyse(BT_raw) %>% 
  kbl(caption = "Comparison with BuyseTest (Follow-up Only)") %>% 
  kable_paper("hover", full_width = FALSE)
```

This comparison confirms that the `infuse` influence-function engine correctly identifies "wins" based on the good = "low" parameter, yielding identical point estimates to the traditional pairwise comparison method.


## Time-to-Event (Survival) Outcomes.

One of the greatest advantages of `infuse` is that it treats survival outcomes with the same mathematical engine as continuous data. By using the complement of the Kaplan-Meier estimator (1−KM) as the Empirical CDF, the package seamlessly integrates censoring into the NTB/WR framework.

### The `ipilimumab` Dataset

The aim of this study was to assess the use of ipilimumab after radiotherapy in patients with metastatic castration-resistant prostate cancer that progressed after docetaxel chemotherapy. Ipilimumab is a fully human monoclonal antibody that binds cytotoxic T-lymphocyte antigen 4 to enhance antitumour immunity. Participants were randomly assigned in a 1:1 ratio to receive bone-directed radiotherapy (8 Gy in one fraction) followed by either **ipilimumab** 10 mg/kg or **placebo** every 3 weeks for up to four doses. The outcome considered here was Progression-Free Survival in months (the censor indicator is `event`)

**Step 1: sow() — The 1−KM Approach**

In `infuse`, survival outcomes are parsed using the standard `survival::Surv(time, event)` syntax. Unlike continuous data where every observation "jumps" the ECDF by exactly $1/n$ (if no ties are present), survival data is more nuanced. The `infuse` engine uses the Kaplan-Meier product-limit formula to determine the size of the jumps.

```{r}
data(ipilimumab)
dat_surv <- ipilimumab

# Sow the survival data
# We specify 'good = "high"' because longer survival is better
s_surv <- sow(Surv(time, event) ~ arm, 
              data = dat_surv, 
              treated = "ipilimumab", 
              good = "high")
```


The `plot()` method for a survival sow outcome displays the ECDF as $1−S_{KM}(t)$. 

```{r}
plot(s_surv)
```

**Step 2: harvest() — Clinical Thresholds in Time**

In oncology, a tiny difference in PFS (e.g., 2 days) might not be clinically meaningful. With `harvest()`, we can set a threshold $\lambda$. If we set $\lambda=3$ months, a treated patient only "wins" the comparison if they remained progression-free for at least 3 months longer than the control patient.

```{r}
# Setting a 3-month clinical relevance threshold
h_surv <- harvest(s_surv, lambda = 3)
summary(h_surv)
```

**Step 3: reap() — Win Ratio & Net Treatment Benefit**

Because the engine is consistent, the output for survival data is identical in format to our previous examples.

```{r}
results_surv <- reap(h_surv)

results_surv %>% 
  kbl(caption = "PFS Analysis (3-Month Threshold)") %>% 
  kable_styling(bootstrap_options = "striped")
```

**Benchmarking with BuyseTest**

We validate the `infuse` results against the `BuyseTest` package using the type = "timetoevent" endpoint. You will notice that the results are almost identical, confirming that the influence function approach for survival data is both accurate and robust.

```{r}
library(BuyseTest)
dat_surv <- dat_surv %>% mutate(arm = factor(arm,levels=c("placebo","ipilimumab")))
BT_surv <- BuyseTest(data = dat_surv, 
                     endpoint = "time", 
                     type = "timetoevent",      # Specify survival type
                     status = "event",   # Specify censoring indicator
                     treatment = "arm", 
                     threshold = 3, 
                     trace = 0)

helper_buyse(BT_surv) %>% 
  kbl(caption = "Comparison with BuyseTest (Survival Data)") %>% 
  kable_paper("hover", full_width = FALSE)
```

**Summary of Survival Benefits**

By treating survival as an ECDF-based distribution (1−KM):

1. Consistency: You use the same functions for PFS as you do for Birthweight or Seizure counts.

2. Censoring Aware: The engine naturally accounts for censored data through the Kaplan-Meier weights.

3. Threshold Modeling: You can quantify "Net Treatment Benefit" in terms of time (months/days), providing an interpretation that is often more intuitive than a Hazard Ratio.


## Combining Multiple Outcomes: The Non-Prioritized Approach

In many trials, a treatment might be "good" for one outcome but "neutral" or even "bad" for another (e.g., an effective drug with side effects). To get a complete picture, we can combine multiple variables into a Global Net Treatment Benefit.

`infuse` uses the Non-Prioritized Outcome (NPO) approach. Instead of ranking outcomes in a strict hierarchy, we assign each one a clinical weight. The global result is a weighted average of the individual benefits.

### `obstetrics` Revisited: Efficacy + Safety

Let's combine two outcomes from the obstetrics dataset:

1. `PretermYN`: Whether the birth was preterm (0 = Yes, 1 = No). Here, low is good.

2. Birthweight: The weight of the baby. Here, high is good.

We will set a threshold of $\lambda=0.5$ for the binary outcome and $\lambda=500g$ for birth weight.

```{r}
dat <- obstetrics %>% mutate(Preterm01 = if_else(PretermYN=="Yes",1,0)) %>% na.omit()
# Step 1: Sow with multiple outcomes
# Note: good = c("low", "high") because we want fewer preterm births 
# and higher birth weights.
s_multi <- sow(Preterm01 + Birthweight ~ Group, 
                data = dat, 
                treated = "T", 
                good = c("high", "high"))

# Step 2: Harvest with two lambdas
h_multi <- harvest(s_multi, lambda = c(0.5, 500))

# Step 3: Reap with equal weights (50/50)
r_multi <- infuse::reap(h_multi, w = c(0.5, 0.5))

r_multi %>%  filter(Variable=="NPO") %>% arrange(Metric,Variable) %>% 
  kbl(caption = "Global Analysis: Preterm Birth & Birthweight") %>% 
  kable_styling(bootstrap_options = "striped")
```


**Interpreting the "NPO" Row**

The `reap()` output adds a final row labelled NPO. This represents the "Global" treatment effect:

* **Global Net Benefit**: If the individual outcomes are $NB_{preterm}=0.10$ and $NB_{weight}=0.05$, an equally weighted NPO will result in a Global NB of 0.075.

* **Clinical Utility**: This NPO allows you to conclude whether the treatment is beneficial on balance, considering both the reduction in preterm births and the increase in birth weight simultaneously.

**Benchmarking NPO: `infuse` vs. `BuyseTest`**

To validate our global assessment, we compare the infuse NPO results with the `BuyseTest` package. While `BuyseTest` is often used for hierarchical (prioritized) testing, it can be configured to perform a weighted non-prioritized analysis by setting the weights for each endpoint.

```{r}
BT_npo <- BuyseTest(data = dat, 
                    formula = Group ~ bin(PretermYN) + cont(Birthweight, threshold = 500),
                    #weightEndpoint = c(0.5, 0.5),      # Equal weights
                    hierarchical = FALSE , 
                    trace = 0)

# Use the helper to format and compare
helper_buyse(BT_npo) %>% kbl() %>% kable_paper("hover")
```


**Customizing the "Clinical Voice"**

If clinicians believe that preventing a preterm birth is twice as important as the birth weight, you can easily adjust the weights in the reap() function:



